### 2019-09-17 2019_neurips_vigil/appendix_model.tex
reorganizing appendix

\section{VWM model}

@@

\section{Basic layers/modules}

@@

\section{VWM cell}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{img/model2}
	\label{fig:model2}
\end{figure}

\begin{figure}
	\includegraphics[width=\textwidth]{img/image}
	\label{fig:model}
\end{figure}

@@

\section{Training and Implementation Details}

\subsection{Training and testing Methodology}

@@

@@

The first approach was to train a model on the hard training set, and test it on the hard test set. This is the same approach used by the COG paper ~\cite{yang2018dataset} to evaluate performance on the hard dataset. We achieve a test accuracy of 91.9 \% which represents a 12\% improvement from the COG model score (see Table 1).
%It shows that SAMNet's design choices make a difference when it come to harder tasks with longer sequences and more distractors objects.

@@

A more granular analysis of accuracy per task shows a major improvement for the two hardest tasks, AndCompareShape and AndCompareColor. Those two tasks represent a higher level of difficulty due to the number of objects to be remembered in order to answer the question correctly.
As we can see in Table 1 we could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard dataset.
The large improvement in these memory-intensive tasks indicate that the SAMNet's external memory plays a crucial role in our results. 
The training and implementation details are in appendix.

\begin{table}[t]
\caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~\cite{yang2018dataset} 
	while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}}
\centering
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{lcccccccccc}
	\toprule
	Model & & SAMNet & && && COG&& \\
	\cmidrule{2-5} \cmidrule{7-11} 
	&&&&& & paper & ours & ours & paper&\\
	\cmidrule{7-9} \cmidrule{10-11}
	Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
	Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
	Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
	\midrule

@@

\begin{table}[!t]
\caption{COG Dataset parameters for the canonical setting and the hard setting  }
\centering
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{ccccccc}
	\toprule

@@

>>>>

\subsection{VWM model}

@@

\subsection{Basic layers/modules}

@@

\subsection{VWM cell}

@@

@@

\subsection{Training and Implementation Details}

\subsubsection{Implementation Details}

@@

\subsubsection{Training and testing Methodology}

@@

The first approach was to train a model on the hard training set, and test it on the hard test set. This is the same approach used by the COG paper ~\cite{yang2018dataset} to evaluate performance on the hard dataset. We achieve a test accuracy of 96.1 \% which represents a 16\% improvement from the COG model score (see Table 1).
%It shows that SAMNet's design choices make a difference when it come to harder tasks with longer sequences and more distractors objects.

@@

A more granular analysis of accuracy per task shows a major improvement for the two hardest tasks, AndCompareShape and AndCompareColor. Those two tasks represent a higher level of difficulty due to the number of objects to be remembered in order to answer the question correctly.
As we can see in Table 1 we could achieve a 12\% improvement for the canonical data set and almost a 30\% improvement for the hard dataset.
The large improvement in these memory-intensive tasks indicate that the SAMNet's external memory plays a crucial role in our results. 
The training and implementation details are in appendix.

\begin{table}[htb]
\caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~\cite{yang2018dataset} 
	while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}}
\centering
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{lcccccccccc}
	\toprule
	Model & & SAMNet & && && COG&& \\
	\cmidrule{2-5} \cmidrule{7-11} 
	&&&&& & paper & ours & ours & paper&\\
	\cmidrule{7-9} \cmidrule{10-11}
	Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
	Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
	Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
	\midrule

@@

\begin{table}[htb]
\caption{COG Dataset parameters for the canonical setting and the hard setting  }
\centering
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{ccccccc}
	\toprule

@@

\subsection{Visualization}

\begin{figure}[!htb]
	\includegraphics[width=\textwidth]{img/model2}
	\label{fig:model2}
\end{figure}

\begin{figure}[!htb]
	\includegraphics[width=\textwidth]{img/image}
	\label{fig:model}
\end{figure}
